\textbf{\sc Deliberative Autonomy for Marine Robotics}

### 2012-01-25 trunk/results.tex
updates

\begin{figure}[htpb]
\centering
\includegraphics[width=0.5\textwidth]{figs/inl.jpg}
\caption{\small An Intermediate Nepheloid Layer (INL) detected by an
  AUV mission in the Monterey Bay in August 2005, showing the location
  of the AUV transect in the bay (left) and optical backscatter image
  at the 420 Nm frequency showing the INLs patchy nature
  (right). \emph{Image courtesy: John Ryan, MBARI}}
\label{fig:inl}
\end{figure}

@@

More interesting experiments are being carried out as a basis to track
more dynamic features such as ocean fronts \cite{fronts11} and
tracking more capable drifting platforms. In particular experiments
with a profiling CTD instrument, the \texttt{Wirewalker}
\cite{rainville01,pinkel11} are resulting in new modalities of making
Lagrangian and Eulerian observations. Fig. \ref{sep11-wirewalker}
shows one such experiment in September 2011 with a GPS-enabled
\texttt{Wirewalker} was tracked by the Dorado running \rx. We are
currently investigating spatio-temporal correlations of CTD data
obtained by the \texttt{Wirewalker} and tying it to the observations
made in the contextual environment by the Dorado's sensors.

>>>>

\begin{figure}[htpb]
\centering
\includegraphics[scale=0.65]{figs/inl.jpg}
\caption{\small An Intermediate Nepheloid Layer (INL) detected by an
  AUV mission in the Monterey Bay in August 2005, showing the location
  of the AUV transect in the bay (left) and optical backscatter image
  at the 420 Nm frequency showing the INLs patchy nature
  (right). \emph{Image courtesy: John Ryan, MBARI}}
\label{fig:inl}
\end{figure}

@@

More interesting experiments are being carried out as a basis to track
more dynamic features such as ocean fronts \cite{fronts11} and
tracking more capable drifting platforms. In particular experiments
with a profiling CTD instrument, the \texttt{Wirewalker}
\cite{rainville01,pinkel11} are resulting in new modalities of making
Lagrangian and Eulerian observations. Fig. \ref{sep11-wirewalker}
shows one such experiment in September 2011 with a GPS-enabled
\texttt{Wirewalker} was tracked by the Dorado running \rx. We are
currently investigating spatio-temporal correlations \cite{gneiting07}
of CTD data obtained by the \texttt{Wirewalker} and tying it to the
observations made in the contextual environment by the Dorado's
sensors.
